Dynein project log

### 2016-09-30 thesis_stuff/thesis_stuff.tex
Add brief Imamula paper notes to tehsis_stuff.pdf.

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\item Fix generate-stepping-data non-printing bug.
\end{itemize}
\end{document}

>>>>

\subsection{Imamula Stepping Model}
This is an older (2007) paper presenting a chemical model. It gives more MT dissociation constants for several different dyneins, and averages them as: $K_{d,pre} = 0.2uM$, $K_{d,post} > 10uM$. They determine these by adding a known concentration of Dynein apo, ATP, ADP-Pi or ADP, adding microtubules, removing MT-Dynein dimers and remeasuring concentration. These parameters are good in that equilibrium constants (as opposed to rate constants) \textit{don't} take into account kinetics, only free energy change...right?\\

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\item Make Dynein binding rate diagram showing how our model relates to the Imamula one
\item Make pretty dynein visualization in PyMol (or some software) showing how dimerization happens AND how docking to the MT happens; ask David what this should look like
\end{itemize}
\end{document}
